GVN-Hoist: Hoisting Computations from Branches

### 2016-08-10 hoist.tex
partition

In our current implementation we partition the list at the point where the
legality checks fail.

@@

Bottom up: Sort the basic blocks of potentially redundant computations
based on DFS-in numbers.  TODO: Explain why sorting by DFS-in numbers.
Then start evaluating the safety checks for first two, if good then
move to second one. That way we can even partially hoist computations
should we find that we cannot remove all the redundant computations.

We can also split the set of to partially hoist multiple times, if
hoisting globally is not possible.

>>>>

In our current implementation we keep as many candidates in one set as possible
unless (greedy approach). We split the list at a point where the legality checks
fail to hoist subset of candidates which are legal to hoist and, start finding
new hoisting point for the remaining ones.

@@
